---
title: "Automatic labeling comparisson - Online appendix"
author: "Teodor Fredriksson, David Issa Mattos, Jan Bosch, Helena Holmström Olsson"
date: "`r format(Sys.time(), '%d %B, %Y')`"
site: bookdown::bookdown_site
documentclass: book
output:
  bookdown::gitbook: default
---


# Preface {-}

This is the analysis of the paper

The environment was defined and based on the `renv` package. The `renv` package logs all the packages in the `renv.lock` file and manages installation for a specific project. For more information see documentation for renv
To replicate this environment, after downloading this repository, type:

```{r, eval=F, echo=T}
renv::hydrate()
```

This command will download and install all the the packages use in this work. Note that it will install the packages only for this project. 

## Compiling this document {-}

This document was created with the `bookdown` package. To compile it (and run every command to generate the models, figures and etc. ) use the custom function from the utils.R file.

```{r eval=F}
compile_book()
```

